\SW: II. Did we beat the lens finding robots in CFHTLS?

### 2014-08-21 doc/acknowledgments.tex
Copied files from simpaper directory

We are also grateful to Brooke Simmons, David Hogg, XXX and YYY for many
useful conversations about citizen science and gravitational lens
detection. % Need to cross-ref with Zooniverse author list
%
PJM was given support by the Royal  Society, in the form of a research
fellowship. 
% He would like to thank the DotAstronomy community for
% introducing so many valuable concepts and tools, and David Harris and
% Roger Davies for valuable conversations about community-building.
%
% AV \ldots
%
% AM \ldots
%
% Zooniverse / Sloan Foundation.
%
The \sw project is open source, and was developed at
https://github.com/drphilmarshall/SpaceWarps.

>>>>

We are also grateful to Brooke Simmons, David Hogg, XXX and YYY for many useful
conversations about citizen science and gravitational lens detection. % Need to
cross-ref with Zooniverse author list
%
PJM was given support by the Royal  Society, in the form of a research
fellowship, and by the U.S. Department of Energy under contract number DE-AC02-76SF00515.
% He would like to thank the DotAstronomy community for
% introducing so many valuable concepts and tools, and David Harris and
% Roger Davies for valuable conversations about community-building.
%
% AV \ldots
%
% AM \ldots
The work of AM and SM was supported by World Premier International Research
Center Initiative (WPI Initiative), MEXT, Japan.
%
% Zooniverse / Sloan Foundation.
%
The \sw project is open source, and was developed at
https://github.com/drphilmarshall/SpaceWarps.
